### 2014-02-22 paper/retrofit.tex
threads
kappa

\and
\inferrule[T-app]
{ } {| conf tS ((\x.te) tv) ~> conf tS ({tv/x} te) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (if true then te1 else te2)  ~> conf tS te1|}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (if false then te1 else te2)  ~> conf tS te2|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', iniTE' (lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}

>>>>

\and
\inferrule[T-app]
{ } {| conf tS ((\x.te) tv) -> conf tS ({tv/x} te) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (if true then te1 else te2) -> conf tS te1|}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (if false then te1 else te2) -> conf tS te2|}

@@

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|fresh (id')|\\
|iTE' THole = iniTE (lconf id il tS id'), THole|
}
{|
iS, iniTE (lconf id il tS (fork ie))
.-.>
iS', iniTE' (lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}
